*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-10 Code/Manuscript_O2.Rmd
changed 2 versus to vs. in text for consistency

```{=tex}
\begin{equation}
  P(λ) = A(λ) × E(λ) 
  (\#eq:WeightedPUR)
\end{equation}
```
Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from
actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation
\@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR),
E(λ) is the imposed growth light emission spectrum from equation
\@ref(eq:WeightedPUR) and PAR is the actinic peak light level (µmol
photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
calculated peak PUR (µmol photons m^-2^ d^-1^) versus actinic
peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
waveband (nm).

@@

```{=tex}
\begin{equation}
  Cumulative~diel~PUR = \frac{PUR × 3600 × Photoperiod}{2}
  (\#eq:SumPURDay)
\end{equation}
```
Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
the black solid line and shaded area, in relation to the actinic PAR,
the dotted line, under each actinic spectral wavebands for *P. marinus*
MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
versus actinic PAR for each *P. marinus* and each spectral waveband.

>>>>

```{=tex}
\begin{equation}
  P(λ) = A(λ) × E(λ) 
  (\#eq:WeightedPUR)
\end{equation}
```
Actinic PUR levels (µmol photons m^-2^ s^-1^) were calculated from
actinic PAR (µmol photons m^-2^ s^-1^) levels using the equation
\@ref(eq:PUR) from [@morelAvailableUsableStored1978]; where P(λ) is the
weighted PUR absorbance spectrum from equation \@ref(eq:WeightedPUR),
E(λ) is the imposed growth light emission spectrum from equation
\@ref(eq:WeightedPUR) and PAR is the actinic peak light level (µmol
photons m^-2^ s^-1^). Figure (\@ref(fig:PurParPlot)) shows the
calculated peak PUR (µmol photons m^-2^ d^-1^) vs. actinic
peak PAR (µmol photons m^-2^ s^-1^) for each strain and each spectral
waveband (nm).

@@

```{=tex}
\begin{equation}
  Cumulative~diel~PUR = \frac{PUR × 3600 × Photoperiod}{2}
  (\#eq:SumPURDay)
\end{equation}
```
Figure \@ref(fig:OverlayPlots) provide visual representations of PUR,
the black solid line and shaded area, in relation to the actinic PAR,
the dotted line, under each actinic spectral wavebands for *P. marinus*
MED4 (A,B,C), SS120 (D,E,F) and MIT9313 (G,H,I). Figure
(\@ref(fig:PurParPlot)) shows the relationship between calculated PUR
vs. actinic PAR for each *P. marinus* and each spectral waveband.
